---
title: "Fair Market Rent Difference: A Spatial Analysis of Unfair Housing Prices"
author: "Dylan Micheals & Shouro Shuvit"
format: pptx
editor: visual
---

## Introduction

-   **Problem**: Housing prices are often unfair and unaffordable

-   **Current Policy**: Fair Market Rent (FMR) is used to determine housing prices

    -   Problem is that it only looks at a narrow portion of what influences housing prices

-   **Goal**: Analyze the difference between FMR and actual housing prices to identify areas of unfair housing prices

## Simulation
```{r,message=FALSE, results = "hide", warning=FALSE, output = FALSE}
source("../Simulation/GWR_simulation.R")
```

```{r,fig.fullwidth = TRUE,fig.align='left'}
ggplot(voronoi_polys)+
  geom_sf(aes(fill = beta_bathrooms),
                  color = scales::alpha("black",
                                alpha = 0.1))+
  scale_fill_viridis_c(name = "Coefficient Value")+
  theme_bw()
```

## Methods

-   **Data**: 100k apartments for Rent Classified Dataset
-   **Data**: FMR Dataset
-   **Analysis**:
    -   **Exploratory Data Analysis**: Analyze correlations between variables and create a basic linear model
    -   **Random Forest**: Predict housing prices based on bedrooms, bathrooms, square footage, and population
    -   **Geographically Weighted Regression**: Predict housing prices based on bedrooms, bathrooms, square footage, and population
    
## Methods

-   **Model Choice**: GWR was chosen because it accounts for spatial autocorrelation which was crucial in our understanding of how the covariates vary over space

## Results

-   **Insert Plots here**
-   **Show where in the US we see our greatest discrepancies**
-   **The validity of our results**

## Discussion

-   **What do our results mean?**
-   **Why are some areas more unfair than others?**
    -   New York City, Western Coast, Colorado, Miami
-   **How can we use this information to make housing more affordable?**
    -   Information can be used to pinpoint

## Conclusion

-   We see in the aforementioned areas that there are other factors that the FMR cannot capture

-   **Moving forward, what can we do to improve upon our research**
