---
title: "Fair Market Rent Difference: A Spatial Analysis of Unfair Housing Prices"
author: 
  name: "Dylan Micheals & Shouro Shuvit"
  institution: "Texas A\\&M University"
format: 
  beamer:
    include-in-header: 
      - text: "\\definecolor{TAMUMaroon}{HTML}{500000}"
      - text: "\\setbeamercolor{palette primary}{bg=TAMUMaroon,fg=white}"
    theme: metropolis
    keep-tex: true
    linkcolor: blue
editor: visual
date: today
---

## Introduction

-   **Problem**: Housing prices are often unfair and unaffordable

-   **Current Policy**: Fair Market Rent (FMR) is used to determine housing prices

    -   Problem is that it only looks at a narrow portion of what influences housing prices

-   **Goal**: Analyze the difference between FMR and actual housing prices to identify areas of unfair housing prices

## Methods

-   **Data**: 100k apartments for Rent Classified Dataset
-   **Data**: FMR Dataset
-   **Analysis**:
    -   **Exploratory Data Analysis**: Analyze correlations between variables and create a basic linear model
    -   **Random Forest**: Algorithmic model used for its predictive accuracy and
    -   **Geographically Weighted Regression**: Predict housing prices based on bedrooms, bathrooms, square footage, and population

## Simulation

```{r,message=FALSE, results = "hide", warning=FALSE, output = FALSE}
source("../Simulation/GWR_simulation.R")
```

```{r,fig.fullwidth = TRUE,fig.align='left'}
library(tidyverse)
library(ggpubr)

ggplot(voronoi_polys)+
  geom_sf(aes(fill = abs(simulation_results$residual)),
                    color = scales::alpha("black",
                                alpha = 0.1))+
  scale_fill_viridis_c(name = "Absolute Error")+
  ggtitle(label = "Absolute Error of Price")
```

## Methods

-   **Model Choice**: GWR was chosen because it accounts for spatial autocorrelation which was crucial in our understanding of how the covariates vary over space

## Results

```{r, message=FALSE, results = "hide", cache=TRUE, warning=FALSE}
source("../Analysis/GWR_Project.R")
ggplot(model_results)+
  geom_sf(aes(fill = re_scale_diff), name = "Price difference",
                    color = scales::alpha("black",
                                alpha = 0.1))+
  scale_fill_viridis_c(name = "Difference in $")+
  ggtitle(label = "Predicted Price difference using Exponential kernel")

```

## Discussion

-   **What do our results mean?**
    -   As per usual the coasts were more expensive than the interior of the country
    -   We can see why for reasons that our model could not capture
-   **How can we use this information to make housing more affordable?**
    -   Information can be used to pinpoint places in the United States FMR policy doesn't meet the needs of the people

## Point of Interest

-   New York City
    -   Density/Population

```{=html}
<!-- -->
```
-   West Coast
    -   Zoning Laws that inhibit housing

```{=html}
<!-- -->
```
-   Denver
    -   Mountanous Geography

```{=html}
<!-- -->
```
-   Miami
    -   Affluent Buyers pricing the locals

## Conclusion

-   We see in the aforementioned areas that there are other factors that the FMR cannot capture

-   **Moving forward, what can we do to improve upon our research**
